Corpus Stats

### 2019-03-26 notebooks/corpus_stats_and_plots.Rmd

```{r}
library(reshape2)
library(ggplot2)
library(ggrepel)

count_df <- readRDS("../data/final_loc_counts.RDS")

total_recorded_sigs <- readRDS("../data/final_recorded_sigs_by_package.RDS")

>>>>

```{r}
library(reshape2)
library(ggplot2)
library(ggrepel)
library(tidyverse)

count_df <- read_rds("../data/final_loc_counts.RDS")
total_recorded_sigs <- read_rds("../data/final_recorded_sigs_by_package.RDS")
